Assumptions of Physics overview: \\ Classical mechanics and infinitesimal reducibility

### 2020-10-27 Overviews/Classical mechanics/ClassicalMechanicsOverview.tex
Added bib

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	urlcolor=blue,
	linkcolor=blue
}
\urlstyle{same}

@@

The overall argument can be summed up in the following diagram that can be used as a guide throughout this note.

@@

>>>>

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	citecolor=blue,
	urlcolor=blue,
	linkcolor=blue
}
\urlstyle{same}

@@

The overall argument (see \cite{AoPPhy1,AoPBook} for more details) can be summed up in the following diagram that can be used as a guide throughout this note.

@@

\bibliography{bibliography}
